\documentclass{contract}
\usepackage{lipsum}

\lang     {english}
\title    {Agreement of T3 Peer Revision Partnership}
\subtitle {In accordance with AP Research}
\date     {January 26, 2024}
\header   {Contract of T3 Partnership}

\begin{document}

\h{General}
This contract is entered into by Ojas Chaturvedi and Saianshul Vishnubhaktula, herein referred to as the 'Partners', for the purpose of establishing a structured and effective peer revision partnership during Trimester 3 of the AP Research course.

\hh{Identification of Partners}
\begin{itemize}
    \item Partner 1: Ojas Chaturvedi
    \item Partner 2: Saianshul Vishnubhaktula
\end{itemize}

\hh{Mission Statement}
The mission of this partnership is to collaboratively enhance the quality of our research papers and presentations through regular, constructive peer review. We aim to provide each other with insightful feedback, drawing on our unique perspectives and academic strengths to foster a supportive and productive learning environment.

\hh{Detailed Plan for Meetings and Communication}
\begin{itemize}
    \item Meeting Frequency: We commit to weekly meetings to ensure continuous progress and timely feedback. Weekly meetings are chosen over bi-weekly or monthly meetings to maintain a consistent rhythm in our collaboration, allowing for more immediate addressing of issues and keeping pace with the ongoing demands of our research projects.
    \item Communication Channels: Meetings will alternate between in-person discussions and digital communications (email, text, or online chat) to accommodate varying schedules and project phases.
    \item Agenda for Meetings: Each meeting will have a pre-determined agenda, including review of recent work, discussion of feedback, and planning for upcoming tasks.
    \item Emergency Contact: In case of urgent matters, we agree to be reachable via phone or instant messaging.
\end{itemize}

\hh{Collaboration and Feedback}
\begin{itemize}
    \item Each partner agrees to provide honest, respectful, and constructive feedback on the other's work.
    \item We will focus on both content and presentation aspects, ensuring clarity, coherence, and academic integrity in our work.
    \item We commit to being receptive to feedback and incorporating it into our work to the best of our abilities.
\end{itemize}

\hh{Confidentiality and Intellectual Property}
\begin{itemize}
    \item All shared work and discussions will remain confidential and will not be disclosed to third parties without mutual consent.
    \item We respect each other's intellectual property and will not use the other's work without proper attribution.
\end{itemize}

\hh{Accountability, Amendments, and Termination}
\begin{itemize}
    \item This agreement signifies our commitment to the terms outlined herein and our dedication to supporting each other's academic endeavors.
    \item Amendments to this contract can be made with mutual consent and should be documented in writing.
    \item The partnership may be terminated by mutual agreement or if either partner consistently fails to meet the agreed-upon terms.
\end{itemize}

\anchor{center}{
    \sign{Ojas Chaturvedi}{High School Student}
    \sign{Saianshul Vishnubhaktula}{High School Student}
}

\end{document}
